Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-10 paper/structureScene.tex
reformulate first paragraph
* avoid repetitions of « interest », « area »
* the subordinate clause precedes the principal clause
* fix grammar

\IEEEPARstart{O}{ver} the past decades, the amount of audio data recorded from our sonic environment has considerably grown. Recent research areas such as eco-acoustics \cite{ECOACOUSTICS2014, krause} start to consider massive deployment of acoustic sensors around the world in order to measure potential animal biodiversity modification over large temporal scales due to human activity or climate change \cite{warren2006urban, NessSST13, stowell13a, stowell13b}.

Also, some recent works demonstrate the interest of such approaches for the characterization of human acoustic pleasantness in urban areas \cite{lafayPartI, guyot2005urban, ricciardi2015sound} and the prediction of annoyance due to traffic \cite{gloaguen}. We believe that those case study are of interest for the signal processing community as they have strong societal impacts and raises interesting research avenues.

>>>>

\IEEEPARstart{T}{he} amount of audio data recorded from our sonic environment has considerably grown over the past decades.
In order to measure the modification of animal biodiversity due to human activity or climate change, the research field of eco-acoustics \cite{ECOACOUSTICS2014, krause} is recently undertaking the massive deployment of acoustic sensors throughout the world \cite{warren2006urban, NessSST13, stowell13a, stowell13b}.
In addition, some recent works demonstrate the interest of acoustic monitoring for the characterization of human pleasantness in urban areas \cite{lafayPartI, guyot2005urban, ricciardi2015sound} as well as the prediction of annoyance due to traffic \cite{gloaguen}.
Because they bear a strong societal impact and raise many scientific challenges, we believe that these case studies are of interest for the signal processing community.
